### 2015-01-05 Docs/architecture/architecture.tex
fix typo
add a note about ghost cells for the base state

>>>>

Note there are no ghost cells for the base state outside of the
physical domain.  For plane-parallel, multilevel simulations, there
are ghostcells at the jumps in refinement---these are filled by the
\code{fill\_code\_base} routine.  The convention when dealing with the
base state is that we only access it inside of the valid physical
domain.  Any multi-dimensional quantity that is derived using the base
state then has its ghost cells filled by the usually \multifab\ ghost
cell routines.
